---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

## geochecker

An R package that lets you check the accuracy of geocoded coordinates using a [Shiny gadget](http://shiny.rstudio.com/articles/gadgets.html).

**Author:** [Lincoln Mullen](http://lincolnmullen.com)<br>
**License:** [MIT](http://opensource.org/licenses/MIT)

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/geochecker)](http://cran.r-project.org/package=geochecker)
[![Travis-CI Build Status](https://travis-ci.org/lmullen/geochecker.svg?branch=master)](https://travis-ci.org/lmullen/geochecker)
[![Coverage Status](https://img.shields.io/codecov/c/github/lmullen/geochecker/master.svg)](https://codecov.io/github/lmullen/geochecker?branch=master)


### Installation

To get the development version from GitHub, use  [devtools](https://github.com/hadley/devtools).

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("lmullen/geochecker")
```

### Contributing

Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
